Summary

### 2015-10-30 inst/examples/summary.Rmd
ok

[Accepted publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.tab)

[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.tab)

@@

[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.tab)

[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.tab)

>>>>

[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv)

[Converted publishers](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_conversion.csv)

@@

[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)

[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)
